Approximation as Differentiation notes

### 2025-02-22 notes/definitions.tex
Clarifying self-enrichment of CMon.

We note that if a category $C$ is \emph{$\CMon$-enriched}, we have that:
\begin{enumerate}
\item Every hom-object $\Hom{C}{A}{B}$ is a commutative monoid; the unit $\zero_{A,B}$ is a zero morphism and
the binary operation $+_{A,B}$ is addition of morphisms.
\item Composition is \emph{biadditive}, i.e.~given by a family of morphisms $\Hom{C}{B}{C} \tensor
\Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$ that preserve the additive structure in $\Hom{C}{B}{C}$ and
$\Hom{C}{A}{B}$ separately:

@@

$\CMon$ is closed monoidal, and so enriched over itself. Thus every hom-object $\CMon(A,B)$ is a commutative
monoid where:
\begin{enumerate}
\item unit $0$ is the constant homomorphism sending every element of $A$ to $\varepsilon_B$;
\item addition of morphisms $+$ is defined pointwise so that $+_{A}$ so that $(f + g)(a) = f(a) + g(a)$.
\end{enumerate}

>>>>

We note that if a category $C$ is \emph{$\CMon$-enriched}, we have that:
\begin{enumerate}
\item Every hom-object $\Hom{C}{A}{B}$ is a commutative monoid of morphisms; we write $\zero_{A,B}$ (zero
morphism) for the unit, and $+_{A,B}$ (addition of morphisms) for the binary operation.
\item Composition is \emph{biadditive}, i.e.~given by a family of morphisms $\Hom{C}{B}{C} \tensor
\Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$ that preserve the additive structure in $\Hom{C}{B}{C}$ and
$\Hom{C}{A}{B}$ separately:

@@

$\CMon$ is closed monoidal, and so enriched over itself. Thus every hom-object $\CMon(A,B)$ is a commutative
monoid of commutative monoid homomorphisms where:
\begin{enumerate}
\item the unit $0$ is the constant homomorphism sending every element of $A$ to $\varepsilon_B$;
\item addition of morphisms $+$ is defined pointwise so that $(f + g)(a) = f(a) + g(a)$.
\end{enumerate}
